Project Uccle

### 2020-06-09 project.Rmd
improvements on ARIMA report and some plots

plot_grid(
  autoplot(aggregated) + labs(title="Timeseries", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(b=-6, unit="pt")),
  autoplot(ts(season.24$figure, frequency=1)) + labs(title="Daily seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(ts(season.168$trend, frequency=168)) + labs(title="Trend", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(l=4, b=-6, unit="pt")),
  autoplot(ts(season.168$figure, frequency=1)) + labs(title="Weekly seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + labs(title="Residuals", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(t=-6, b=-6, unit="pt")),
  autoplot(season.168$figure + rep(season.24$figure, 7)) + labs(title="Weekly seasonality (sum)", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  nrow = 3,
  greedy = T)

>>>>

plot_grid(
  autoplot(aggregated) + labs(title="Timeseries", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(b=-6, unit="pt")),
  autoplot(ts(season.24$figure, frequency=1)) + labs(title="Daily seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(ts(season.168$trend, frequency=168)) + labs(title="Trend", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(l=4, b=-6, unit="pt")),
  autoplot(ts(season.168$figure, frequency=1)) + labs(title="Weekly seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + labs(title="Residuals", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(t=-6, b=-6, unit="pt")),
  autoplot(season.168$figure + rep(season.24$figure, 7)) + labs(title="Composed seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  nrow = 3,
  greedy = T)

### 2020-06-09 project.mems.Rmd
improvements on ARIMA report and some plots

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

>>>>

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)") + xlab(seasonality.xlab))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

### 2020-06-09 project.uccs.Rmd
improvements on ARIMA report and some plots

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

>>>>

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)") + xlab(seasonality.xlab))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))
